The interaction of very high energy cosmic rays with the Earth's atmosphere produces extensive electromagnetic particle cascades. This superluminal shower of particles emits photons of blue wavelength, commonly known as Cherenkov radiation. The \gls{iact} technique enables the probing of the universe at \si{TeV} energies through the detection of these Cherenkov showers. The \glsf{cta} will represent the next leap forward in \gls{vhe} astronomy, improving on the sensitivity of current \glspl{iact} by a factor of \change{find value}. A major component of \gls{cta} are the \glspl{sst}, which extend the detection capabilities of \gls{cta} up to \SI{300}{TeV}\change{check value}, entering an energy region previously inaccessible by \glspl{iact} \change{check this, and see if it extends beyond just iacts}. 

One of three proposed designs for the \gls{sst} is the \glsf{gct}. Utilising a dual-mirror Schwarzschild-Couder optical design, \gls{gct} enables a \SI{9}{\degree} \gls{fov} for a compact camera design. The camera developed for \gls{gct} is the \glsf{chec}. Two prototypes for \gls{chec} have been built, each utilising different compact photosensor technology. \gls{chec-m} features \glspl{mapmt}, a pixelised extension of the \gls{pmt} technology extensively used by \glspl{iact}. \gls{chec-s} features \glspl{sipmt}, a novel photosensor which utilises semiconductor technology for photon counting over a large dynamic range. To fully utilise the signal output from these photosensors, and allow the opportunity for future data analysis procedures to be exploited, the entire signal received from these photosensors are digitised into waveforms following a trigger. These waveforms have a length of 96 samples with nanosecond precision.

In this thesis, the full calibration and signal-extraction pipeline currently adopted by \gls{chec} to reliably extract the Cherenkov signal from the waveforms is presented. The resulting performance of these procedures, and of the camera designs, is explored with respect to the requirements specified by the \gls{cta} Observatory. Potential improvements to the camera and calibration implementations are identified, and simulations of \gls{chec} are utilised to demonstrate the performance increase these proposals provide. Consequently, an improvement to the photosensor that would allow the \gls{chec-s} prototype design to comfortably meet the \gls{cta} requirements is specified. Testing of these improvements is anticipated to commence in late 2018 \change{check data}. Finally, the results of the second on-telescope campaign for the \gls{chec-m} camera are presented, during which observations of Cherenkov showers and optical measurements of Jupiter were conducted.


\change{reset acronyms}