First and foremost, I would like to thank my supervisor, Prof Garret Cotter, for the immense amount of opportunities you have given me during my DPhil. I am eternally grateful for the support you have given me, while simultaneously letting me find my own route to develop into an independent researcher.

A major amount of thanks goes to Dr Richard White, for all the assistance you have provided me in the last four+ years, and for all the helpful and interesting discussions, even at odd times of the day. I really appreciate all the time you have invested in me, and all the patience you have shown me. It has all helped me improve and develop myself into a contributing, invested, and hopefully valuable member of the team.

I would like to thank Prof Jim Hinton for introducing me to CHEC and CTA, through the multiple summer placements you offered me while I studied for my MPhys degree at the University of Leicester. Those placements sparked my love for programming, and have led me down this prosperous academic path. Furthermore, I am grateful for the host at the Max-Planck-Institut für Kernphysik during 9~months of my DPhil. I make no secret about how much I loved my time there, and it truly advanced my proficiency as a researcher. I look forward to my continued interaction with MPIK.

A big thanks to all the GCT members, past and present, who enriched not only my work, but also my personal life. Specifically, I would like to thank Andrea De Franco, Tom Armstrong, and Heide Costantini. You three have been some of the biggest help I have from an early point in my DPhil. Furthermore, a big thanks to all those who took the time to proofread my thesis - Tom, Connor, Christoph, Paul, Rich and Garret. You were all a huge help and seriously reduced the stress I was under.

During my journey through undergrad, I met some amazing people who continue to give me immense amounts of happiness and support. Thank you Magda, Ben, Vili, and Viki. 

Mum and Dad, you have always believed in me, and you have always encouraged me to be my best. Thank you Mum for all the times we sat together revising for my exams, and thank you Dad for the incessant reminders to keep on top of my homework. 

Wiebke, you have been my biggest support during the writing of my thesis. I am so grateful for everything you do. Thank you so much for sacrificing so much of your time to proofread this work. Your advice and reassurances were probably the most valuable thing I received during the past few months. Thank you for being the best partner I could possibly ask for.
