\chapter{\label{ch9-summary}Summary} 

The utilisation of the \gls{iact} technique for \gls{vhe} astronomy has been introduced, alongside the description of \gls{cta}'s intention to become the most sensitive \gls{iact} array to date. This ambitious goal will be attained with the construction of the largest ever \gls{iact} array, exploiting the latest developments in optics, photosensors, computational potential \change{better way to say this?}, and Cherenkov shower analysis techniques. Observations of the highest energy phenomena in the universe will be facilitated by the \glspl{sst}, for which \gls{gct} is one of three designs proposed.

The photosensors, electronics, and digitisation procedures of the \gls{gct} camera, known as \gls{chec}, have been described, with a focus on the factors that influence the signal measured from the photosensors. It was identified that the factor most likely to impede the performance of the \gls{chec-m} prototype (which utilises \glspl{mapmt} as the photosensor) is the poor photoelectron resolution that is apparent in \gls{pmt} technology. This arises due to the fluctuations in the secondary multiplication factor at each dynode in the chain. Conversely, in the \gls{chec-s} prototype, which features excellent photoelectron resolution due to its \gls{sipmt} photosensor, the characteristic most likely to limit the performance is the high optical crosstalk of \SIrange{35}{40}{\percent}. The phenomena of optical crosstalk occurs when secondary photons (generated during the electron-hole avalanche) cause additional avalanches in neighbouring microcells. These pitfalls of each photosensor are characterised in terms of their \gls{enf}. The next production of \glspl{sipmt} for the \gls{chec} prototypes are expected to have an optical crosstalk of \SI{\sim 10}{\percent}, thereby overcoming this limitation in performance.

A description of the \gls{cta} Consortium and Observatory was provided, along with the requirements defined by the observatory to ensure that the science goals of \gls{cta} are met. This thesis primarily focussed on the \textit{Charge Resolution} performance criteria, and its associated \gls{cta} requirement. The \textit{Charge Resolution} is a measure of how well the Cherenkov shower signal can be reconstructed, thereby quantifying the performance of the calibration, charge extraction, and the camera design into a single value per illumination level. Additionally, the data flow model within \gls{cta} was described. This is adhered to by the waveform processing procedures I have developed.

Due to their importance in the waveform processing and Cherenkov shower reconstruction, the software packages relevant to \gls{chec} were outlined. This included the \pkg{TargetCalib} library, used to perform the calibration required for waveform data obtained with the \gls{target} modules. It also included \pkg{ctapipe}, a Python library developed by \gls{cta} consortium members to be utilised as the low-level data processing pipeline. This purpose encapsulates the transformation of calibrated waveform data obtained from the camera, into event lists containing the characteristics of the progenitor particle which created the Cherenkov shower detected by the array. Finally, the stimulation packages, important tools in the \gls{cta} array design and shower reconstruction, were also detailed.

A significant proportion of my contributions towards the commissioning of \gls{chec} have been in the development of a calibration pipeline for the digitised waveform data. The first components included in this calibration are the pedestal subtraction and Transfer Function corrections, required for waveforms obtained from the \gls{target} module to remove the storage cell dependence of the samples. The second component of the calibration is the conversion of the photosensor signal into photoelectrons, and the flat-fielding of the signal response across the camera. This ensures that each pixel reports the same charge on average for a certain number of photons. An initial attempt at the recovery of saturated charges has also been shown, however this is an area where further investigation is required.

The step following the calibration of the waveforms is the extraction of the Cherenkov signal embedded within them. This process is typically split into two procedures: peak finding and charge extraction. This signal extraction process is not only a common \gls{iact} procedure, but also a generic signal processing exercise. Consequently, many methods already exist to achieve this. The typical approaches used by \glspl{iact} have been described, alongside my implementation of a \textit{Cross Correlation} extraction method, designed to reliably extract the pulse in the presence of uncorrelated noise. The result of the charge extraction is a single value per pixel, forming the image of a Cherenkov shower, which often appears as an ellipse. The conventional method to parametrise this image is the expression of the image in terms of its second moments, commonly known as the \textit{Hillas Parameters}. These parameters enable the properties of the progenitor particle to be inferred, including its trajectory, energy, and classification. The latter property is used to exclude the prevalent hadronic shower background, while the former two provide information about the astrophysical source that produced the gamma-ray.

In the context of the \gls{cta} Requirements, the performance of the \gls{chec-s} prototype was explored. To fully perform this investigation, an updated simulation model that accurately represents \gls{chec-s} was generated. While the measurements from the constructed \gls{chec-s} prototype do not appear to meet the \textit{Charge Resolution} requirement, even in the absence of \gls{nsb}, the corresponding simulated lab measurements do suggest it is possible to meet the requirements with the current design. The cause of the discrepancy in results between the real measurements and simulations it currently unknown, however reductions in the bias voltage applied to the \gls{sipmt} suggest it may be connected to the optical crosstalk, while investigation into the pulse shape suggest it could be correlated with a changing \gls{fwhm} of the pulse with amplitude. Regardless, an investigation into the improvement of \textit{Charge Resolution} via a reduction in optical crosstalk is performed in three ways: with simulations of a \gls{chec-s} prototype with \SI{20}{\percent} optical crosstalk; by reducing the bias voltage (and therefore the overvoltage) across the \glspl{sipmt}; and analytically, using the equation that represents the \textit{Charge Resolution} requirement curve, which encapsulates the contributions from the electronic and \gls{nsb} noise, \gls{enf}, and the miscalibration. In all three investigations, it is observed that the \textit{Charge Resolution} requirement will be comfortably achieved with a \gls{chec-s} prototype that contains \glspl{sipmt} with the lower optical crosstalk of at least \SI{20}{\percent}. A comparison against the \textit{Charge Resolution} performance achieved with \gls{chec-m} was also conducted. This displayed the improvement one would expect in going from \gls{chec-m} to \gls{chec-s}, due to the reduction of \gls{enf} between the respective photosensors.

Finally, the results from the second on-telescope campaign for \gls{chec-m} were presented. This campaign included both observations of Cherenkov showers, and optical measurements of Jupiter using the increase in the variance of the waveform baseline. An inconsistency in the results obtained from each of the observation types, compared to results obtained from simulations, each independently suggested the camera was installed a couple of millimetres out-of-focus. \change{find out from Heide about how much}. An updated simulation that better reflected the true \gls{psf} of the camera during the campaign was created, resulting in Cherenkov shower images that more closely represented those measured by the camera. 
 
\subsection{Outlook}
 
The full review within the context of the remaining \gls{cta} Requirements is necessary to prove \gls{chec} can be accepted as an in-kind contribution to the \gls{cta} Observatory. This is a large undertaking, requiring the accumulation of work from the entire \gls{chec} group. An important aspect of this review is the full validation and verification of the Monte Carlo model of the \gls{chec} prototype, which must ensure there are no disparities between the simulations and the data. This process will involve the identification of the additional noise factor observed in the non-simulated dataset.

We shall begin testing the latest production of \glspl{sipmt} from Hamamatsu on the \gls{chec-s} prototype in early 2019. During this testing, the \textit{Charge Resolution} investigation will be revisited to confirm the predictions made by this thesis.

The finalisation of the calibration procedure of \gls{chec} is intended. This includes the production of a processing chain that can perform the required operations at rates required by the \gls{cta} Observatory. This development will include the production of a procedure to directly generate \textit{R1} \gls{tio} files during data taking (i.e. online calibration), as opposed to generating \textit{R0} \gls{tio} and calibrating offline. Furthermore, the Transfer Function calibration could benefit from further development, as better performance at low amplitudes should be achievable (see Appendix~\ref{a4-tf}). Finally, the two major factors currently missing from the calibration chain are the consideration of how the corrections change with temperature, and the correction of saturated measurements. There will be a primary focus for future investigations into improving the calibration performance.

The next on-telescope campaign is anticipated for November 2018, when the \gls{chec-s} prototype will be transported to Mt. Etna, Sicily, to be integrated on to the \gls{astri} telescope structure for 2 weeks. During this campaign, priority will be given to formalising the operation procedure, and fully characterising the trigger efficiency of the telescope in the presence of \gls{nsb}.